A Continuation-Based Solution\break of the Linearity Challenge

### 2025-12-29 paper/Context.lagda.tex
global revision

When splitting a context $\Context$ into $\ContextD + \ContextE$, for each type
in $\Context$ we use one of the prefix operators \AgdaInductiveConstructor{<}
and \AgdaInductiveConstructor{>} to indicate whether the type is meant to be
placed in $\ContextD$ or in $\ContextE$.
%
For example, below is a proof of the splitting $\Splitting{[A, B, C,
D]}{[B]}{[A, C, D]}$.

@@

% It is often the case that the context $\ContextD$ in a splitting
% $\Splitting\ContextC\ContextD\ContextE$ is a singleton list $[A]$. We use this
% particular splitting to describe the presence of a channel of type $A$ in
% $\ContextC$ and giving a name $\ContextE$ to the residual context. For this
% particular case, we introduce the dedicated notation
% $\SimpleSplitting\ContextC{A}\ContextE$ which we find clearer.

% \begin{code}
% _∋_⊳_ : Context → Type → Context → Set
% Γ ∋ A ⊳ Δ = Γ ≃ [ A ] + Δ
% \end{code}
\begin{code}[hide]
+-empty-l : ∀{Γ Δ} → Γ ≃ [] + Δ → Γ ≡ Δ
+-empty-l • = refl
+-empty-l (> p) = cong (_ ∷_) (+-empty-l p)
\end{code}

@@

It is easy to prove that $\ContextC$ is unrestricted if so are $\ContextD$ and
$\ContextE$ when $\Splitting\ContextC\ContextD\ContextE$:

>>>>

When splitting a context $\Context$ into $\ContextD + \ContextE$, for each type
in $\Context$ we use one of the prefix operators \AgdaInductiveConstructor{<}
and \AgdaInductiveConstructor{>} to indicate whether the type is meant to be
placed in $\ContextD$ or in $\ContextE$. Once we reach the end of the typing
context, we use the constructor \AgdaInductiveConstructor{•} to build the
trivial splitting of the empty context into two empty partitions.
%
For example, below is a proof of the splitting $\Splitting{[A, B, C,
D]}{[B]}{[A, C, D]}$.

@@

\begin{code}[hide]
+-empty-l : ∀{Γ Δ} → Γ ≃ [] + Δ → Γ ≡ Δ
+-empty-l • = refl
+-empty-l (> p) = cong (_ ∷_) (+-empty-l p)
\end{code}

@@

The empty context is trivially unrestricted. A non-empty context is unrestricted
if its head has the form $\WhyNot A$ for some $A$ and provided that its tail is
unrestricted as well.
%
It is easy to prove that $\ContextC$ is unrestricted if so are $\ContextD$ and
$\ContextE$ when $\Splitting\ContextC\ContextD\ContextE$:

### 2025-12-29 paper/agda.tex
LCP => LCC
global revision
tuning related and repo references

In this section we describe the formalisation of \LCP in Agda. We present in
detail only some key parts of the code including the representation of types and
processes, the definition of the operational semantics and the statement of the
main results. The interested reader may find the complete source code in the
public repository.

>>>>

In this section we describe the formalisation of \LCC in Agda. Each of the
following sub-sections matches one of the modules of the formalisation. We
present in detail only some key parts of the code including the representation
of types and processes, the definition of the operational semantics and the
statement of the main results. The complete source code is available in \LCC's
public repository~\cite{PadovaniRaffaelli25}.
